The language of generalization: Probability, vagueness, and interaction

### 2018-09-24 paper/response.tex

\begin{document}

\begin{letter}

\opening{Dear Professor Saxe,}

Thank you for soliciting peer reviews for our manuscript \emph{The Language of Generalization}. We appreciate the time both you and the reviewers have devoted to commenting and critiquing our manuscript. We are grateful for the opportunity to resubmit a revised version to be considered for publication in \emph{Psychological Review}.
We have made a number of substantive changes in this version of the manuscript that we hope will improve the readability of the paper.

Inspired by Reviewer 1's request to see the presentation of the various puzzles in a more accessible form,
we have merged the General Discussion subsection ``Other philosophical puzzles'' with the worked examples (e.g., \emph{birds lay eggs vs. are female}, \emph{mosquitos carry malaria}) that appeared before the experiments; now, both appear before the experiments.
We describe why each example is interesting, how the model handles each case., and provide a summary in a table (per R1's suggestion).
By moving these other philosophical puzzles to appear before the experiments, we are able to foreshadow the relevance of \emph{predictive probability} (and motivate Expt. 2c).

We have taken Reviewers 1 and 3's suggestion of reconfiguring some of the general discussion material so now a comparison to other theories appears before the experiments (after the model section and worked examples).
We have also tightened this discussion, hopefully addressing R3's uncertainty about the relationship of our theories to extant theories. 
Our theory is, in R3's option-space, either (e) an outright alternative to prior theories, or (d) a more precise specification of (at least some aspects of) prior theories, namely Cohen (1999)'s domain-restriction theory and Leslie (2007)'s cognitively-based context sensitivity.
This equivocation comes because these previous theories admit different interpretations, only some of which are compatible with ours.
This is hopefully now more clearly articulated.
Finally, we include an additional subsection in the ``alternative theories'' section describing the various alternative quantitative models we will use for model comparison (in the hope of addressing R3's 2nd comment). 
The importance of these quantitative comparisons is slightly orthogonal to the comparisons to Leslie, Cohen, and other linguistic theories: These quantitative comparisons provide assurance that our model is not overparameterized and that the prior in our model is not doing all of the work. 
This also allows us to clarify the sense in which our model is unique (R3's 3rd comment): It is the first model of generics that makes quantitative predictions about human endorsements (and it does so by connecting with a truth-conditional semantic theory in a particular way).

We tremendously appreciate Reviewer 2's thoughtful exposition on our account and have incorporated a number of their insights and suggestions into the General Discussion.
We have added a discussion about how accepting a generic sentence adds to the common ground information about cue validity, which suggests other empirical tests of the accounts.
We have noted as R2 does that there have been no empirical tests of the analogy between habituality and genericity, and that our formal machinery shows the way in which the two can be thought of as the same kind of linguistic phenomena.
We have taken a few paragraphs to clarify the kind of vagueness we have in mind for generics, namely what R2 had in mind: vagueness and genericity are analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertainty as to the exact truth conditions. 
We note that, from a modeling perspective, this sort of ``lexical uncertainty`` is kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity). 
We clarify that the confluence of underlying mechanisms between generic vagueness and adjectival vagueness doesn't imply that generic vagueness has all the features of the adjectival kind (which indeed it probably doesn't -- for instance Sorites sequences).
We additionally now discuss one interpretation of the uncertain threshold, drawing a connection explicitly to Williamson (1992)'s epistemicist view.\footnote{
	R2 actually cited Williamson (1994). In our searches, however, we could only find a 1998 book chapter published in the Encyclopedia of Cognitive Science, a book published in 2002, both under the title ``Vagueness'', and a paper in 1992 called ``Vagueness and Ignorance'' written with Peter Simons. 
}

In addition to these broad theoretical points, we have tried to clarify a number of smaller points brought up by Reviewer 1.
We have been more explicit in our relation of generics with quantifiers as being from a purely semantic perspective, not taking into account pragmatic interpretations
We have removed our argument from analogy about states of uncertainty being more fundamental than states of certainly.
This point is a very particular one relating to Leslie (2007; 2008)'s theory and rhetoric; we now express the same idea by noting that our uncertain threshold model can be viewed as a formalization of Leslie's notion of a \emph{default generalization}. 
We have maintained our discussion of the acquisition of the semantics of generics because it has been a topic of interest to developmental psychologists (and central to Leslie's account), but we have cleaned up the prose and made explicit the way in which we believe learning generic language facilitates learning quantified semantics (in short: they share the same logical form, but generics are simpler because they lack a fixed threshold).

things i'm not sure about:
\begin{enumerate}
\item property theories of meaning (R1) \ndg{they are alluding to theories of concepts -- conceptual role, feature-based, etc. i think we can add a few comments to the section on relation to conceptual theories of generics about this. basically we are not committed to any particular theory of concepts, as long as they are able to yield quantitative feature probabilities.} \mht{i didn't feel completely confident writing about theories of concepts and don't have a sense of ``standard`` citations that would convey succinctly our point. can you add this?}
\end{enumerate}

### 2018-09-26 paper/case1-generics.Rmd
clean up case 1; until rsa model results section

We first investigate how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g. "Mosquitos carry malaria."),  noncharacteristic features displayed by a minority (e.g., "Robins are female."), and features that are totally absent (e.g. "Lions lay eggs.").
We further craft sentences with the goal of eliciting the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt. 1a).
We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p)$.
The prevalence elicitation procedure (Expt. 1b) includes measurements of the referent-prevalence $p$ for different categories  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to generate predictions for the endorsement model (Eq. \ref{eq:S1}) as well as for simpler, alternative models.

@@

As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
indeterminate generics were endorsed at a rate \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).

In addition to these categorical differences between our thirty generic statements, we find a continuum of endorsement values (Figure\ \@ref(fig:generics-endorsement-figure)A).
Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and all shades in between.
We next measure the prevalence prior distribution and use them to articulate a set of quantitative models that try to predict this quantitative variability in endorsements.

@@

The prevalence prior $P(p)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g., \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are walking around and you come across an instance of your favorite kind of animal from Earth (e.g., a peregrine falcon). 
Ask yourself "is it female?" 
Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female peregrine falcons, i.e., 50\%). 
Now, do you think it lays eggs? 
Your answer to this question will likely depend upon on what animal you're thinking of: If you're thinking of a peregrine falcon, the probability is similar to that of being female (50\%) because female peregrine falcons lay eggs; if you're thinking of a mammal, it's likely that it won't lay eggs (0\%) because most mammals give birth to live young. 
That is, the answer is roughly either 50\% or 0\% depending on the kind of creature you are thinking of.^[
  The subjective probability may, in fact, be non-zero and small as opposed to 0. 
  Non-zero probabilities allow for the intuitive possibility of a mammal animal that generally reproduces by giving live birth which in fact lays eggs, potentially explained by some strange generic mutation.
]

This thought experiment decomposes the prevalence prior $P(p)$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(p \mid k)$.
We will use this decomposition to measure the prevalence prior $P(p) = \int_{k} P(p \mid k) \diff k$ and build a structured statistical model to accurately reconstruct the prevalence prior.
We measured prior distributions empirically for the set of properties (e.g., *lays eggs, carries malaria*; 21 in total) used in our generic sentences in Expt. 1a.
To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").

@@

On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt. 1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five of their own (Figure\ \@ref(fig:generics-prior-task)A).
A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%"; Figure\ \@ref(fig:generics-prior-task)B).
Eight property--columns in total appeared in the table.

This whole procedure was repeated two times (two trials).
In total, each participant generated ten animal names and reported on the prevalence of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve).

@@

The elicited prior distributions have a diversity of shapes (8 examples shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)A) that are roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure\ \@ref(fig:simulations)A).
The property *being female* is present in almost all categories in almost exactly the same proportion, whereas properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions. 
*Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
This diversity is important because our endorsement model makes different predictions depending on the shape of the distrubution.

@@

<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
In order to integrate the results of this prior measurement task into our model of endorsement, we must build a statistical model of the prior elicitation data.
We approximate the prevalence distribution for each property (e.g., \textsc{lay eggs}) with a Mixture of Betas model, which assumes that the data generated for each kind comes from one of two underlying Beta distributions.^[
  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
] 
We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.^[
  This assumption is similar in spirit to that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
]
This "null distribution" is potentially present for all features in exactly the same way (i.e., the lack of producing the feature).
The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
<!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
For more details about model implementation and inference, see Appendix C.

@@

We can now compute the predictions of our endorsement model; we first articulate a set of alternatives: models that have been previously proposed in the literature, an alternative form of our proposed endorsement model, and our full endorsement model.

@@

From the prevalence prior data (Expt. 1b), we estimate participants' beliefs about the referent prevalence (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}) and use it to predict endorsement.
We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet). 
Referent prevalence alone does okay at predicting these data because our stimulus set includes generics that are true with high prevalence properties (e.g., "Leopards have spots.") and false with low prevalence properties (e.g., "Leopards have wings.").

@@

Cue validity indexes the diagnosticity of the feature for a kind, given formally by the probability of a kind given the feature $P(k \mid f)$.
As discussed in the Computational Model section above, cue validity is linearly related to expected value of the prevalence prior distribution (see Appendix A for derivation).
Cue validity thus is similar to a *point estimate* of the prevalence prior distribution, a single metric that collapses across the full distribution. 
<!-- Comparison to a model based on cue validity thus  -->

<!-- To show that the full distribution over prevalence is important, we explore a secondary baseline model based on prevalence and cue validity. -->
Though the cue validity of a property for a category can be derived from the prevalence prior distribution, previous empirical studies have estimated cue validity from different empirical sources [@Cree2006; @Khemlani2012].
In the empirical literature on generics, researchers often ask directly about the cue validity probability [e.g., "There is an animal that lays eggs. What is the probability that it is a robin?"; @Khemlani2012], though in the broader literature on semantic memory a *free production* paradigm is often employed [e.g., "X lays eggs. What do you think X is?"; @Cree2006]. 
We found that these two ways of estimating cue validity diverge for a number of key cases (Appendix B).
Most notably, undiagnostic features (e.g., *is female*), which in theory have a cue validity close to zero, were rated as having intermediate cue validity in the *direct question* paradigm. 
In response to a direct question such as "There is an animal that is female. What is probability that it is a robin?", participants could be responding "I don't know" rather than reporting their intuitive base rate that a random animal would be a robin. 
The free production paradigm did not produce artifacts such as this one, and we chose to use it as the more veridical estimate of cue validity. 
For a detailed analysis of the different cue validity measurements and comparison to cue validity derived from the prevalence prior, see Appendix B.

@@

A linear model that uses predictors for both referent-prevalence and cue validity does a better job at explaining the endorsement data than just prevalence alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
This model is able to account for the endorsements of examples like "Mosquitos carry malaria" (model endorsement and bootstrapped-95\% confidence interval = `r round(reg.mosquitos.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.carry[[1,"prediction_ci_upper"]], 2)`]) and "Lions have manes" (`r round(reg.lions.manes[[1,"prediction_mean"]], 2)` [`r round(reg.lions.manes[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.lions.manes[[1,"prediction_ci_upper"]], 2)`])), as these features are very diagnostic of the kind (human endorsement both $> 0.9$).
Deviations, however, still remain.
For example, "Robins lay eggs" still receives only intermediate endorsement by this model (`r round(reg.robins.lay.eggs[[1,"prediction_mean"]], 2)` [`r round(reg.robins.lay.eggs[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.robins.lay.eggs[[1,"MAP_h"]], 2)` [`r round(reg.robins.lay.eggs[[1,"low"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"high"]], 2)`]), and "Mosquitos don't carry malaria" is misjudged to be a pretty good statement (`r round(reg.mosquitos.dont.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.mosquitos.dont.carry[[1,"MAP_h"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"low"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"high"]], 2)`]).

"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of reducing structured prevalence prior distributions to single point-estimates of cue validity.
*Lays eggs* is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like *robins*.
Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (Figure\ \@ref(fig:simulations)A bottom).
Furthermore, cue validity glosses over the difference between "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction).
Such a model makes the wrong prediction for non-distinctive properties with high referent prevalence (e.g., "Mosquitos don't carry malaria").
A simple metric like cue validity is too blunt to capture these subtleties.

@@

Our underspecified-threshold model considers how well the generalization would bring a naive interpreter's prior distribution on prevalence $P(p)$ (Eq. \ref{eq:L0}; e.g., the prevalence of laying eggs among other animals) in line with the referent prevalence ($p$ in Eq. \ref{eq:S1}; e.g, the prevalence of laying eggs among robins).
There are several substantive components to this hypothesis: (a) context in the form of a prior distribution over prevalence $P(p)$, (b) endorsement as a decision-theoretic process of uttering the generalization vs. not uttering it, and (c) vagueness in the semantics of a generalization.
We construct an alternative, lesioned model by removing the vagueness in meaning, assigning a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keeping the prior and the decision-theoretic architecture in place. 
There are no correspondingly simple ways to lesion the other two components (context or speaker decision) while still producing a model that makes quantitative, context-sensitive predictions.

<!-- The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter. -->
For each of these communicative endorsement models, we build a joint Bayesian data analysis model of the referent prevalence $p$, prevalence priors $P(p)$ (both from Expt. 1b data), and the endorsement data (Expt. 1a). 
Empirically elicited referent prevalence and prevalence prior data (Expt. 1b) directly constrain the parameters that generate those quantities in the model ($p$ in Eq. \ref{eq:S1} and $P(p)$ in Eq. \ref{eq:L0}, respectively). 
The prevalence prior $P(p)$ is modeled as a mixture of Betas while referent prevalence is modeled by a single Beta distribution.
The endorsement data (Expt. 1a) is modeled by our endorsement model (Eq. \ref{eq:S1}), which has one free parameter $\lambda$.
Predicting the data from both Expt. 1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix C and Figure\ \@ref(fig:genericsModelDiagram) for further model specification details).
To learn about the credible values of the parameters of the joint-inference model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 150,000 iterations, discarding the first 50,000 for burn-in.

>>>>

We first investigate how the *uncertain threshold* endorsement model predicts actual human endorsements of generic statements.
We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g. "Mosquitos carry malaria."),  noncharacteristic features displayed by a minority (e.g., "Robins are female."), and features that are totally absent (e.g. "Lions lay eggs.").
We further craft sentences with the goal of eliciting the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt. 1a).
We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p)$.
The prevalence elicitation procedure (Expt. 1b) includes measurements of the referent-prevalence $p$ for different categories  (e.g., $P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to generate predictions for the endorsement model (Eq. \ref{eq:S1}) as well as for simpler, alternative models.

@@

As a manipulation check, the first author assigned an \emph{a priori} truth judgment (true/false/indeterminate) to each stimulus item.
As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
indeterminate generics were endorsed at a rate \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).

Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and the gradedness between the extremes.
We observe gradedness among our thirty examples covering a continuum of endorsement values (Figure\ \@ref(fig:generics-endorsement-figure)A).
Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
We next measure the prevalence prior distribution and use them to articulate a set of quantitative models that try to predict this quantitative variability in endorsements.

@@

The prevalence prior $P(p)$ in Eq. \ref{eq:L0} describes the belief distribution on the probability of a given feature (e.g., \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, imagine you are walking outside and come across an instance of your favorite kind of animal (e.g., a reindeer). 
What is the chance it is female?
Your answer will probably depend upon the percentage of the category that you believe to be female (e.g., the percentage of female reindeer, approximately 50\%). 
What is the chance that it lay eggs?
Again, this depends upon the percentage of the category that you believe lays eggs, which then further depends on the particular kind of animal under consideration: If you're thinking of a reindeer, the answer is probably 0\%; if you're thinking of a peregrine falcon, the probability is similar to the being female probability (50%) because female peregrine falcons lay eggs. 
That is, the answer to how many of an arbitrary category is likely to lay eggs is either roughly 50\% or 0\%, depending on the kind of creature you may be thinking of.^[
  The subjective probability may, in fact, be non-zero and small as opposed to 0. 
  Non-zero probabilities allow for the intuitive possibility of a reindeer that, by some terribly improbable set of circumstances such as a genetic mutation, lays eggs.
]

The thought experiment decomposes the prevalence prior $P(p)$ into a prior distribution on kinds $P(k)$ and then a conditional probability of the prevalence given the kind $P(p \mid k)$.
This decomposition can be used to measure the prevalence prior for familiar properties $P(p) = \int_{k} P(p \mid k) \diff k$ as a stand-in for a richer intuitive theory that could give rise to prevalence judgments.
We measured prior distributions empirically for the set of properties (e.g., *lays eggs, carries malaria*; 21 in total) used in our generic sentences in Expt. 1a.
To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").^[
  That is, we implicitly assume for these properties that logical negation tokenizes its own threshold instead of being derived compositionally via bivalent logical negation. For related empirical and modeling investigations regarding resolving compositional vs. non-compositional negation (in the context of gradable adjectives, e.g., "not happy" vs. "unhappy"), see @Tessler2018negant.
]

@@

On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
Participants first were shown six animal categories randomly sampled from a set corresponding to referent-categories of the generic sentences used in Expt. 1a (e.g., \textsc{robins, mosquitos}) and were asked to generate five animal kinds of their own (Figure\ \@ref(fig:generics-prior-task)A).
A column then appeared to the right of the animal names with a property label in the column header (e.g., *lays eggs*).
Participants were asked to fill in each cell with a with the percentage of members of each of the species that had the property (e.g., "50\%"; Figure\ \@ref(fig:generics-prior-task)B).
Eight property--columns in total appeared in the table.
This whole procedure was repeated two times (two trials).
In total, each participant generated ten animal names and reported on the prevalence of sixteen properties for twenty-two animals (their own ten and the experimentally-supplied twelve).

@@

The elicited prior distributions have a diversity of shapes (8 examples shown in Figure\ \@ref(fig:generic-endorsement-priors-figure)A) that are roughly consistent with the schematic prior distributions used in the *Worked Examples* section (Figure\ \@ref(fig:simulations)A).
The property *being female* is present in almost all categories in almost exactly the same proportion, whereas properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions. 
*Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
This diversity is important because our endorsement model makes different predictions depending on the shape of the distrubution.

@@

<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
In order to incorporate the uncertainty in our measurement of the prevalence prior into the endorsement model's predictions, we build a Bayesian statistical model of the prior elicitation data.
We approximate the prevalence distribution for each property (e.g., \textsc{lay eggs}) with a Mixture of Betas model, which assumes that the data generated for each kind comes from one of two underlying Beta distributions.^[
  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
] 
We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.^[
  This assumption is similar in spirit to that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
]
This "null distribution" is potentially present for all features and acts in exactly the same way (i.e., the lack of producing the feature).
The second distribution represents kinds of animals who *could* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
<!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
For more details about model implementation and inference, see Appendix C.

@@

We can now compute the predictions of our endorsement model. 
We describe first the behavior of a set of alternatives: models that have been previously proposed in the literature, an alternative form of our proposed endorsement model, before proceeding to the results of the uncertain threshold endorsement model.

@@

From the prevalence prior data (Expt. 1b), we estimate participants' beliefs about the referent prevalence (e.g., the percentage of \textsc{robins} that \textsc{lay eggs}) and use it to predict endorsement.
We find a little over half of the variance in the endorsement data is explained this way ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev`$; MSE=$`r mse.gen.regression.prev`$; Figure \ \@ref(fig:generic-endorsement-priors-figure), upper-right: lower-left facet). 
Referent prevalence alone predicts a fair amount of variance because our stimulus set includes generics that are true with high prevalence properties (e.g., "Leopards have spots.") and false with low prevalence properties (e.g., "Leopards have wings.").

@@

Cue validity indexes the diagnosticity of the feature for a kind, given formally by the probability of a kind given the feature $P(k \mid f)$.
As discussed in the *Other Theories* section above, cue validity is linearly related to expected value of the prevalence prior distribution (see Appendix A for derivation).
Cue validity thus acts using a *point estimate* of the prevalence prior distribution, a single metric that summarizes the prior distribution. 
<!-- Comparison to a model based on cue validity thus  -->

<!-- To show that the full distribution over prevalence is important, we explore a secondary baseline model based on prevalence and cue validity. -->
Though the cue validity of a property for a category can be derived from the prevalence prior distribution, previous empirical studies of generics have estimated cue validity from different empirical sources [@Cree2006; @Khemlani2012].
In the empirical literature on generics, researchers often ask directly about the cue validity probability [e.g., "There is an animal that lays eggs. What is the probability that it is a robin?"; @Khemlani2012], though in the broader literature on semantic memory a *free production* paradigm is often employed [e.g., "X lays eggs. What do you think X is?"; @Cree2006]. 
We found that these two ways of estimating cue validity diverge for a number of key cases (Appendix B).
Most notably, undiagnostic features (e.g., *is female*), which in theory have a cue validity close to zero, were rated as having intermediate cue validity (around 0.5) in the *direct question* paradigm, but not in the *free production* paradigm. 
In response to a direct question such as "There is an animal that is female. What is probability that it is a robin?", participants seem to want to respond "I don't know" by placing the slider bar at the midpoint, rather than reporting their intuitive base rate that a random animal would be a robin. 
The free production paradigm did not produce artifacts such as this one, and we chose to use it as the more veridical estimate of cue validity. 
For a detailed analysis of the different cue validity measurements and comparison to cue validity derived from the prevalence prior, see Appendix B.

@@

A linear model that uses predictors for both referent-prevalence and cue validity does a better job at explaining the endorsement data than just prevalence alone ($r^2(`r r2.gen.n`) = `r r2.gen.regression.prev.cv`$; MSE=$`r mse.gen.regression.prev.cv`$).
This model is able to account for the endorsements of examples like "Mosquitos carry malaria" (model endorsement and bootstrapped-95\% confidence interval = `r round(reg.mosquitos.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.carry[[1,"prediction_ci_upper"]], 2)`]) and "Lions have manes" (`r round(reg.lions.manes[[1,"prediction_mean"]], 2)` [`r round(reg.lions.manes[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.lions.manes[[1,"prediction_ci_upper"]], 2)`])), as these features are very diagnostic of the kind (generic endorsement both $> 0.9$).
Deviations, however, still remain.
For example, "Robins lay eggs" still receives only intermediate endorsement by this model (`r round(reg.robins.lay.eggs[[1,"prediction_mean"]], 2)` [`r round(reg.robins.lay.eggs[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.robins.lay.eggs[[1,"MAP_h"]], 2)` [`r round(reg.robins.lay.eggs[[1,"low"]], 2)`,
`r round(reg.robins.lay.eggs[[1,"high"]], 2)`]), and "Mosquitos don't carry malaria" is misjudged to be a pretty good statement (`r round(reg.mosquitos.dont.carry[[1,"prediction_mean"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_lower"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"prediction_ci_upper"]], 2)`]; human endorsement = `r round(reg.mosquitos.dont.carry[[1,"MAP_h"]], 2)` [`r round(reg.mosquitos.dont.carry[[1,"low"]], 2)`,
`r round(reg.mosquitos.dont.carry[[1,"high"]], 2)`]).

"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of reducing structured prevalence prior distributions to single point-estimates of cue validity.
*Lays eggs* is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like *robins*.
Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (Figure\ \@ref(fig:simulations)A bottom).
Furthermore, cue validity cannot distinguish "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction); the cue validity can be zero or low for different reasons.
Such a model makes the wrong prediction for non-distinctive properties with high referent prevalence (e.g., "Mosquitos don't carry malaria").

@@

Our underspecified-threshold model considers how well the generalization would bring a naive interpreter's prior distribution on prevalence $P(p)$ (Eq. \ref{eq:L0}; e.g., the prevalence of laying eggs among other animals) in line with the speaker's belief about the referent prevalence ($p$ in Eq. \ref{eq:S1}; e.g, the prevalence of laying eggs among robins).
There are several substantive components to this hypothesis: (a) context in the form of a prior distribution over prevalence $P(p)$, (b) endorsement as a decision-theoretic process of uttering the generalization vs. not uttering it, and (c) vagueness in the semantics of a generalization.
We construct an alternative, lesioned model by removing the vagueness in meaning, assigning a fixed semantics to the generalization (i.e., analogous to the quantified statements) but keeping the prior and the decision-theoretic architecture in place. 
There are no correspondingly simple ways to lesion the other two components (context or speaker decision) while still producing a model that makes quantitative, context-sensitive predictions.

<!-- The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter. -->
For both the fixed-threshold and full uncertain-threshold endorsement models, we build a joint Bayesian data analysis model of the referent prevalence $p$, prevalence priors $P(p)$ (both from Expt. 1b data), and the endorsement data (Expt. 1a). 
Empirically elicited referent prevalence and prevalence prior data (Expt. 1b) directly constrain the parameters that generate those quantities in the model ($p$ in Eq. \ref{eq:S1} and $P(p)$ in Eq. \ref{eq:L0}, respectively). 
The prevalence prior $P(p)$ is modeled as a mixture of Betas while referent prevalence is modeled by a single Beta distribution.
The endorsement data (Expt. 1a) is model by our endorsement model (Eq. \ref{eq:S1}), which has one free parameter $\lambda$.
Predicting the data from both Expt. 1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix C and Figure\ \@ref(fig:genericsModelDiagram) for further model specification details).
To learn about the credible values of the parameters of the joint-inference model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 150,000 iterations, discarding the first 50,000 for burn-in.
